---
title: "Untitled"
output: html_document
---
Exercises
1) Plot distance against stretch.

```{r}
ex1 <- data.frame(stretch=c(46,54,48,50,44,42,52), distance=c(148,182,173,166,109,141,166))
ex1
```

```{r}
ggplot(data=ex1, aes(x=stretch, y=distance)) + geom_bar(stat="identity")
```


2) The follwing data have ten observations taken during the years 1970-79, on October snow cover for Eurasia (snow cover is in millions of square kilometers).

```{r}
ex2 <- data.frame(year=c(1970:1979), snow.cover=c(6.5,12.0,14.9,10.0,10.7,7.9,21.9,12.5,14.5,9.2))
ex2
```

Plot snow.cover versus year.

```{r}
ggplot(ex2, aes(year)) + ggtitle("Plot snow.cover versus year") + geom_line(aes(y = snow.cover, colour = "Cover"), size = 2) + scale_colour_manual(values = c("cornflowerblue")) + scale_x_continuous(breaks = seq(ex2$year[1], ex2$year[length(ex2$year)], by = 1))
```


Plot a histogram of the snow.cover values.

```{r}
ggplot(ex2, aes(x=snow.cover)) + geom_histogram(binwidth=3)
```

3) Given the following data:
```{r}
ex3 = read.table("dataset.txt", header = TRUE, sep = ',', na.strings = 'NR')
```

Create a function to convert ºF to ºC and in (inches) to mm.
C = 5/9 (F - 32)
1 hinches = 25,4 mm
```{r}
ex3.celsiusAnMm <- ex3
ex3.celsiusAnMm[ ,c(2:8)] <- 5/9 * (ex3.celsiusAnMm[ ,c(2:8)] - 32)
ex3.celsiusAnMm[ ,c(9:12)] <- ex3.celsiusAnMm[ ,c(9:12)] * 25.4
ex3.celsiusAnMm
as.data.frame(ex3.celsiusAnMm)
library(ggplot2)
```

Plot Year vs. Warmest Minimum Temperature.
```{r}
pl1 <- ggplot(ex3.celsiusAnMm, aes(Year)) + ggtitle("Plot Year vs. Warmest Minimum Temperature and Coldest Minimum
Temperature")
pl1 <- pl1 + geom_line(aes(y = Warmest.Minimum.Temperature..F., colour = "Warnest"), size = 2)
pl1 <- pl1 + labs(title = "Plot Year vs. Warmest Minimum Temperature", x = "Year", y = "Temperature") 
pl1 <- pl1 + scale_colour_manual(values = c("cornflowerblue")) 
pl1
```
Plot Year vs. Warmest Minimum Temperature and Coldest Minimum
Temperature. Don’t forget to add a legend!
```{r}
pl2 <- ggplot(ex3.celsiusAnMm, aes(Year)) + ggtitle("Plot Year vs. Warmest Minimum Temperature and Coldest Minimum
Temperature")
pl2 <- pl2 + geom_line(aes(y = Warmest.Minimum.Temperature..F., colour = "Warnest"), size = 2)
pl2 <- pl2 + geom_line(aes(y = Coldest.Minimum.Temperature..F., colour = "Coldest"), size = 2)
pl2 <- pl2 + labs(title = "Plot Year vs. Warmest Minimum Temperature and Coldest Minimum
Temperature", x = "Year", y = "Temperature") 
pl2 <- pl2 + scale_colour_manual(values = c("cornflowerblue", "darkslateblue")) 
pl2
```

